BOLD Parameter Estimation Using Particle Filters

### 2010-07-22 doc/thesis/results.tex
got all the new graphics in

\subsection{Single Voxel Review}
\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c |}
\hline 
& \multicolumn{4}{|c|}{Signal} & \multicolumn{4}{|c|}{No Signal}\\
\hline
& \multicolumn{2}{|c|}{Low Noise} & \multicolumn{2}{|c|}{High Noise} 
& \multicolumn{2}{|c|}{$\sigma_y = .001, \sigma_x = .0005$} 
& \multicolumn{2}{|c|}{$\sigma_y = .01, \sigma_x = .005$}\\
\hline 
&$\sqrt{MSR}$ & $N\sqrt{MSR}$ &
 $\sqrt{MSR}$ & $N\sqrt{MSR}$ &
 $\sqrt{MSR}$ & $N\sqrt{MSR}$ &
 $\sqrt{MSR}$ & $N\sqrt{MSR}$ \\
\hline       
\hline       
1 & 0.003211 & 0.478015  & 0.014065  & 1.038941    &0.001667 & 1.295007 & 0.015114 & 1.33641 \\
2 & 0.003055 & 0.531771  & 0.013731  & 0.951648  &  0.001586 & 1.301750 & 0.015510 & 1.336667 \\
3 & 0.003289 & 0.545798  & 0.012754 &  0.995392  &  0.001651 & 1.26287 &  0.013957 & 1.159567 \\
4 & 0.002847 & 0.498237  & 0.016726  & 1.161286  &  0.001506 & 1.431959 & 0.013814 & 1.099876 \\
5 & 0.003006 & 0.468048  & 0.013698 &  1.039724   & 0.001515 & 1.256645 & 0.014350 & 1.201072 \\
6 & 0.002833 & 0.459001  & 0.011495 &  1.002143  &  0.001557 & 1.270797 & 0.013504 & 1.045886 \\
7 & 0.003028 & 0.460962  & 0.015550 &  1.088472   & 0.001585 & 1.154406 & 0.013006 & 1.205429 \\
8 & 0.003044 & 0.518376  & 0.012054 &  1.059620  &  0.001643 & 1.274564 & 0.015446 & 1.122502 \\
9 & 0.003345 & 0.525303  & 0.015104 &  1.015703  &  0.001679 & 1.320244 & 0.014847 & 1.086366 \\
10 & 0.003175 &0.492111  & 0.012493  & 1.189964  &  0.001826 & 1.344562 & 0.013125 & 1.221350 \\
11 & 0.002889 &0.490919  & 0.012165 &  0.953676  &  0.001950 & 1.325223 & 0.014457 & 1.117367 \\
\hline
mean & 0.003066 & 0.497140  & 0.013621 &  1.04514   &  0.001651 & 1.294366 & 0.014285 & 1.175681 \\
\hline
\end{tabular}
\caption{$\sqrt{MSE}$ and the normalized $\sqrt{MSE}$, 
    $\left(\sqrt{MSE}/(\text{Median Absolute Deviation})\right)$ for different configurations.} 
\label{tab:SignleVoxelActivationComparison} 
\end{table}

@@

\begin{figure}[H]
\centering
\subfigure[Region labels for simulated slice.]{
\includegraphics[height=9cm]{images/simregions.png} \label{fig:simslice_mask} }
\subfigure[Residual Heat Map.]{\includegraphics[height=9cm]{images/sim_hm}}
\subfigure[Grey matter map for simulate region.]{\includegraphics[height=9cm]{images/sim_gm}}
\caption{Comparison of activation with greymatter, parameter regions.}
\label{fig:simslice_hm}
\end{figure}

>>>>

\subsection{Single Voxel Review}
\begin{table}[t]
\centering
\begin{tabular}{|c | c | c | c | c | c | c | c | c |}
\hline 
& \multicolumn{4}{|c|}{Signal} & \multicolumn{4}{|c|}{No Signal}\\
\hline
& \multicolumn{2}{|c|}{Low Noise} & \multicolumn{2}{|c|}{High Noise} 
& \multicolumn{2}{|c|}{$\sigma_y = .001, \sigma_x = .0005$} 
& \multicolumn{2}{|c|}{$\sigma_y = .01, \sigma_x = .005$}\\
\hline 
& $M.I.$ & N. Res. &
  $M.I.$ & N. Res. &
  $M.I.$ & N. Res. &
  $M.I.$ & N. Res. \\
\hline       
\hline       
1 & 0.86687 &0.47801 &0.09077 &1.03894 &0.06326  &  1.29501 &0.03024   &1.33641 \\
2 & 0.93975 &0.53177 &0.13767 &0.95165 &-0.01075  & 1.30175 &-0.02677  &1.33667 \\
3 & 0.82382 &0.5458  &0.13505 &0.99539 &0.02345  &  1.26287 &-0.0111   &1.15957 \\
4 & 0.94661 &0.49824 &0.04341 &1.16129 &-0.00906  & 1.43196 &0.00147   &1.09988 \\
5 & 0.94281 &0.46805 &0.13718 &1.03972 &0.00663  &  1.25664 &-0.00204  &1.20107 \\
6 & 0.92539 &0.459   &0.12337 &1.00214 &-0.00816  & 1.2708 & 0.01775   &1.04589 \\
7 & 0.98892 &0.46096 &0.15381 &1.08847 &0.02664  &  1.15441 &0.03163   &1.20543 \\
8 & 0.98796 &0.51838 &0.11325 &1.05962 &0.03285  &  1.27456 &0.01951   &1.1225 \\
9 & 0.8804  &0.5253  &0.09669 &1.0157  &0.01628  &  1.32024 &0.01039   &1.08637 \\
10 & 0.88721 &0.49211 &0.18339 &1.18996 &0.00407  &  1.34456 &0.00508   &1.22135 \\
11 & 0.96644 &0.49092 &0.10949 &0.95368 &0.03323  &  1.32522 &-0.01284  &1.11737 \\
\hline                                                                           
min  & 0.92329 &0.49714 &0.12037 &1.04514 &0.01622  &  1.29437 &0.00576   &1.17568 \\
\hline                                                                           
max & 0.96644 &0.459   &0.10949 &0.95165 &-0.01075  & 1.15441 &-0.01284  &1.04589 \\
\hline                                                                           
mean  & 0.86687 &0.5458  &0.09077 &1.18996 &0.06326  &  1.43196 &0.03024   &1.33667 \\
\hline
\end{tabular}
\caption{Mutual Information and the normalized $\sqrt{MSE}$, 
    for signal/noise configurations.}
\label{tab:SignleVoxelActivationComparison} 
\end{table}

@@

\begin{figure}[H]
\centering
\subfigure[Region labels for simulated slice.]{
\includegraphics[height=9.5cm]{images/simregions.png} \label{fig:simslice_mask} }
\subfigure[Grey matter map for simulate region.]{\includegraphics[height=9.5cm]{images/sim_gm}}
\subfigure[Residual Map. Scale is Normalized $\sqrt{MSE}$.]
{\includegraphics[height=9cm]{images/sim_hm}}
\subfigure[Mutual Information Map. Scale is bits.]
{\includegraphics[height=9cm]{images/sim_hm_mi}}
\caption{Comparison of activation with greymatter, parameter regions.}
\label{fig:simslice_hm}
\end{figure}

### 2010-07-22 doc/thesis/resultsB.tex
got all the new graphics in

\begin{figure}[H]
\subfigure[]{\label{fig:hm_spm} \includegraphics[scale=3]{images/spm_hm}}
\subfigure[]{\label{fig:hm_canon_spm_x} \includegraphics[scale=3]{images/spm_hm_x}}
\subfigure[]{\label{fig:hm_canon_spm_y} \includegraphics[scale=3]{images/spm_hm_y}}
\subfigure[]{\label{fig:hm_canon_spm_z} \includegraphics[scale=3]{images/spm_hm_z}}
\subfigure{\label{fig:scale_spm} \includegraphics[scale=.5]{images/scale1}}
\caption{Sagittal, coronal and axial slices of SPM results (\autoref{fig:hm_canon_spm_x} \autoref{fig:hm_canon_spm_y} 
         \autoref{fig:hm_canon_spm_x}), as well as a series of axial slices, \autoref{fig:hm_spm}. Units
         of activation are in Student's T-scores. Higher indicates higher assurance that the signal cannot
         have occurred through noise alone.}
\label{fig:hm_canon_spm}
\end{figure}

\begin{figure}[H]
\subfigure[]{\label{fig:hm_pfilter} \includegraphics[scale=3]{images/pfilter_hm}}
\subfigure[]{\label{fig:hm_canon_pfilter_x} \includegraphics[scale=3]{images/pfilter_hm_x}}
\subfigure[]{\label{fig:hm_canon_pfilter_y} \includegraphics[scale=3]{images/pfilter_hm_y}}
\subfigure[]{\label{fig:hm_canon_pfilter_z} \includegraphics[scale=3]{images/pfilter_hm_z}}
\subfigure{\label{fig:scale_pfilter} \includegraphics[scale=.5]{images/scale2}}
\caption{Sagittal, coronal and axial slices of SPM results (\autoref{fig:hm_canon_pfilter_x} \autoref{fig:hm_canon_pfilter_y} 
         \autoref{fig:hm_canon_pfilter_x}), as well as a series of axial slices, \autoref{fig:hm_pfilter}. 
         Units of match is normalized error. The lowest (best) levels were $.7$,
         whereas the worst levels could go higher than 100 (not shown).}
\label{fig:hm_canon_pfilter}
\end{figure}

\begin{figure}[H]
\subfigure[]{\label{fig:hm_pfilter85} \includegraphics[scale=3]{images/pfilter85_hm}}
\subfigure[]{\label{fig:hm_canon_pfilter85_x} \includegraphics[scale=3]{images/pfilter_hm85_x}}
\subfigure[]{\label{fig:hm_canon_pfilter85_y} \includegraphics[scale=3]{images/pfilter_hm85_y}}
\subfigure[]{\label{fig:hm_canon_pfilter85_z} \includegraphics[scale=3]{images/pfilter_hm85_z}}
\subfigure{\label{fig:scale_pfilter85} \includegraphics[scale=.5]{images/scale3}}
\caption{Sagittal, coronal and axial slices of SPM results (\autoref{fig:hm_canon_pfilter_x} \autoref{fig:hm_canon_pfilter_y} 
         \autoref{fig:hm_canon_pfilter_x}), as well as a series of axial slices, \autoref{fig:hm_pfilter}. 
         Units of match is normalized $\sqrt{MSE}$. The lowest (best) levels were $.7$,
         whereas the worst levels could go higher than 100 (not shown).}
\label{fig:hm_canon_pfilter85}
\end{figure}

@@

\begin{figure}
\subfigure[Particle Filter]{\label{fig:comp5pfilter} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/5_pfilter_25_34_25}}\\
\subfigure[SPM]{\label{fig:comp5spm} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/5_spm_25_34_25}}
\caption{Section 5, Estimated vs. Actual BOLD response}
\label{fig:comp5}
\end{figure}

>>>>

\begin{figure}[H]
\subfigure[]{\label{fig:hm_spm} \includegraphics[scale=.85]{images/spm_hm}}
\subfigure[]{\label{fig:hm_canon_spm_x} \includegraphics[scale=3]{images/spm_hm_x}}
\subfigure[]{\label{fig:hm_canon_spm_y} \includegraphics[scale=3]{images/spm_hm_y}}
\subfigure[]{\label{fig:hm_canon_spm_z} \includegraphics[scale=3]{images/spm_hm_z}}
\subfigure{\label{fig:scale_spm} \includegraphics[scale=.5]{images/scale1}}
\caption{Sagittal, coronal and axial slices of SPM results (\autoref{fig:hm_canon_spm_x} \autoref{fig:hm_canon_spm_y} 
         \autoref{fig:hm_canon_spm_x}), as well as a series of axial slices, \autoref{fig:hm_spm}. Units
         of activation are in Student's T-scores. Higher indicates higher assurance that the signal cannot
         have occurred through noise alone.}
\label{fig:hm_canon_spm}
\end{figure}

\begin{figure}[H]
\subfigure[]{\label{fig:hm_pfilter} \includegraphics[scale=.85]{images/pfilter_hm}}
\subfigure[]{\label{fig:hm_canon_pfilter_x} \includegraphics[scale=3]{images/pfilter_hm_x}}
\subfigure[]{\label{fig:hm_canon_pfilter_y} \includegraphics[scale=3]{images/pfilter_hm_y}}
\subfigure[]{\label{fig:hm_canon_pfilter_z} \includegraphics[scale=3]{images/pfilter_hm_z}}
\subfigure{\label{fig:scale_pfilter} \includegraphics[scale=.5]{images/scale2}}
\caption{Sagittal, coronal and axial (\autoref{fig:hm_canon_pfilter_x} \autoref{fig:hm_canon_pfilter_y} 
         \autoref{fig:hm_canon_pfilter_x}), as well as a series of axial slices, \autoref{fig:hm_pfilter}. 
         Units of match is normalized residual. The lowest (best) levels were $.7$.
         The highest error shown is $1$.}
\label{fig:hm_canon_pfilter}
\end{figure}

%\begin{figure}[H]
%\subfigure[]{\label{fig:hm_pfilter85} \includegraphics[scale=.75]{images/pfilter85_hm}}
%\subfigure[]{\label{fig:hm_canon_pfilter85_x} \includegraphics[scale=3]{images/pfilter_hm85_x}}
%\subfigure[]{\label{fig:hm_canon_pfilter85_y} \includegraphics[scale=3]{images/pfilter_hm85_y}}
%\subfigure[]{\label{fig:hm_canon_pfilter85_z} \includegraphics[scale=3]{images/pfilter_hm85_z}}
%\subfigure{\label{fig:scale_pfilter85} \includegraphics[scale=.5]{images/scale3}}
%\caption{Sagittal, coronal and axial (\autoref{fig:hm_canon_pfilter_x} \autoref{fig:hm_canon_pfilter_y} 
%         \autoref{fig:hm_canon_pfilter_x}), as well as a series of axial slices, \autoref{fig:hm_pfilter}. 
%         Units of match is normalized residual. The lowest (best) levels were $.7$.
%         The highest error shown is $.85$.}
%\label{fig:hm_canon_pfilter85}
%\end{figure}

\begin{figure}[H]
\subfigure[]{\label{fig:hm_mi} \includegraphics[scale=.85]{images/mi_hm}}
\subfigure[]{\label{fig:hm_canon_mi_x} \includegraphics[scale=3]{images/mi_hm_x}}
\subfigure[]{\label{fig:hm_canon_mi_y} \includegraphics[scale=3]{images/mi_hm_y}}
\subfigure[]{\label{fig:hm_canon_mi_z} \includegraphics[scale=3]{images/mi_hm_z}}
\subfigure{\label{fig:scale_mi} \includegraphics[scale=.5]{images/scale4}}
\caption{Sagittal, coronal and axial (\autoref{fig:hm_canon_pfilter_x} \autoref{fig:hm_canon_pfilter_y} 
         \autoref{fig:hm_canon_pfilter_x}), as well as a series of axial slices, \autoref{fig:hm_pfilter}. 
         Units of match is bits (standard for base-2 Mutual Information). The highest (best) levels are 
         $.42$. The worst shown is $.1$.}
\label{fig:hm_canon_pfilter85}
\end{figure}

@@

% or in original coordinates 29-9-13
\begin{figure}
\subfigure[Particle Filter]{\label{fig:comp5pfilter} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/5_pfilter_29_9_13}}\\
\subfigure[SPM]{\label{fig:comp5spm} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/5_spm_29_9_13}}
\caption{Section 5, Below threshold in both particle filter checks, but above threshold in SPM. Mutual Information of $0.0212822$, T-Value
of $4.17399$ and $MSE$ of $1.14171$.}
\label{fig:comp5}
\end{figure}

%23-10-18 or in original coordinates 36-17-19
\begin{figure}
\subfigure[Particle Filter]{\label{fig:comp5pfilter} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/6_pfilter_36_17_19}}\\
\subfigure[SPM]{\label{fig:comp5spm} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/6_spm_36_17_19}}
\caption{Section 6, MI of $0.335504$, T Value: $2.49154$, normalized error: $0.783348$ Not visible in SPM}
\label{fig:comp5}
\end{figure}

%16-19-0 or in original coordinates 29-26-1
\begin{figure}
\subfigure[Particle Filter]{\label{fig:comp5pfilter} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/7_pfilter_29_26_1}}\\
%\subfigure[SPM]{\label{fig:comp5spm} \includegraphics[clip=true,trim=5cm 1cm 4cm 1cm,width=15cm]{images/5_spm_25_34_25}}
\caption{Section 7, $.1052$ in MI, $1.31534$ in SPM (which left this flat) and $1.09992$ normalized $\sqrt{MSE}$. Only visible in MI map. }
\label{fig:comp5}
\end{figure}
